Bayesian Nonparametric System Reliability\\ using Sets of Priors

### 2016-01-02 ijar-npb-ms.tex
Start writing software bits

To see this,
remember that $\yktz$ gives the prior expected functioning probability for a component of type $k$ at time $t$.
From Equation~\eqref{eq:nyupdate} (right) we see that $\yktn$ is increasing in $\yktz$,
%the posterior parameter set bounds are the transformed prior parameter set bounds,
%i.e., $\yktzu$ corresponds to the upper bound of $\PktN$, for all $\nktz \in \PktZ$,
such that for each fixed $\nktz$, $\yktzu$ will maximise the posterior expected functioning probability $\yktn$.
%
Now, a higher posterior expected functioning probability means
higher probability for many components out of $m_k$ surviving,
i.e., probabilities for the larger $l_k$'s are higher, and in turn for the lower $l_k$'s are lower.
Indeed, the Beta-Binomial distribution is stochastically ordered for varying $\yktn$, i.e.,
its cmf \eqref{eq:postpredCnycmf} is decreasing in $\yktn$ for all $l_k$,
such that the cmfs for different values of $\yktn$ do not cross each other.
This means that for each fixed $\nktz$, the Beta-Binomial cmf \eqref{eq:postpredCnycmf} is minimized for $\yktzu$ in all $l_k$,
such that the probability weights given to high values of $l_k$ are maximised. %for $\yktzu$.
For coherent systems, $\Phi$ is non-decreasing in each of its arguments $l_1,\ldots,l_K$,
thus $\Rsys(t)$ is maximised by putting most probability weight on the highest $l_k$ values for each $k$,
which is in turn obtained for $\yktzu$, $k=1,\ldots,K$.
We therefore have
%
%for a certain $k$, a high probability on high $l_k$'s is never worse than a high probability on lower $l_k$'s,
%keeping all other component type expressions fixed.
%***Monotonicity in $\yz_{k,t}$, so we get, for each $t \in {\cal T}$,
\begin{align*}
\lefteqn{\lRsys(t \mid \vec{t}^1, \ldots, \vec{t}^K)}\\
 &= \min_{\PtZi{1}, \ldots, \PtZi{K}} \Rsys(t \mid \PtZi{1}, \ldots, \PtZi{K}, \vec{t}^1, \ldots, \vec{t}^K) \\
 &= \min_{\nz_{1,t},\ldots,\nz_{K,t}} 
    \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K)
                                                 \prod_{k=1}^K P(C^k_t = l_k \mid \yktzl, \nktz, s^k_t) \\
 &= \min_{\nz_{1,t},\ldots,\nz_{K,t}} 
    \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K) \times \\ & \hspace*{12ex}
    \prod_{k=1}^K {m_k \choose l_k} \frac{B(l_k + \nn_{k,t}\ynl_{k,t}, m_k - l_k + \nn_{k,t}(1-\ynl_{k,t}))}
                                         {B(\nn_{k,t}\ynl_{k,t}, \nn_{k,t}(1-\ynl_{k,t}))} \,.
\end{align*}
In the following, we will give some guidelines on how to choose the parameter sets $\PkZi{1}, \ldots, \PkZi{\tmax}$
which define the set of prior discrete reliability functions for components of type $k$.
We think this is much easier in terms of $\nz$ and $\yz$ than it would be in terms of $\alpha$ and $\beta$.
%***How to choose the sets of priors for the survival function of type $k$ components,
%i.e. how to choose $\PkZi{1}, \ldots \PkZi{\tmax}$?***

@@

%***code published in Louis' \textbf{R} package \texttt{ReliabilityTheory},
The method is implemented in the \textbf{R} package \texttt{ReliabilityTheory} \citep{2015:aslett-RT}
with the function \texttt{nonParBayesSystemInferencePriorSets()};
the package also contains the function \texttt{computeSystemSurvivalSignature()}
to calculate the survival signature for a given system layout (reliability block diagramm).

@@

>>>>

To see this,
remember that $\yktz$ gives the prior expected functioning probability for a component of type $k$ at time $t$.
From Equation~\eqref{eq:nyupdate} (right) we see that $\yktn$ is increasing in $\yktz$,
%the posterior parameter set bounds are the transformed prior parameter set bounds,
%i.e., $\yktzu$ corresponds to the upper bound of $\PktN$, for all $\nktz \in \PktZ$,
such that for each fixed $\nktz$, $\yktzu$ will maximise the posterior expected functioning probability $\yktn$.
%
Now, a higher posterior expected functioning probability means
higher probability for many components out of $m_k$ surviving,
i.e., probabilities for the larger $l_k$'s are higher, and in turn for the lower $l_k$'s are lower.
Indeed, the Beta-Binomial distribution is stochastically ordered for varying $\yktn$, i.e.,
its cmf \eqref{eq:postpredCnycmf} is decreasing in $\yktn$ for all $l_k$,
such that the cmfs for different values of $\yktn$ do not cross each other.
This means that for each fixed $\nktz$, the Beta-Binomial cmf \eqref{eq:postpredCnycmf} is minimized for $\yktzu$ in all $l_k$,
such that the probability weights given to high values of $l_k$ are maximised. %for $\yktzu$.
For coherent systems, $\Phi$ is non-decreasing in each of its arguments $l_1,\ldots,l_K$,
thus $\Rsys(t)$ is maximised by putting most probability weight on the highest $l_k$ values for each $k$,
which is in turn obtained for $\yktzu$, $k=1,\ldots,K$.
We therefore have
%
%for a certain $k$, a high probability on high $l_k$'s is never worse than a high probability on lower $l_k$'s,
%keeping all other component type expressions fixed.
%***Monotonicity in $\yz_{k,t}$, so we get, for each $t \in {\cal T}$,
\begin{align}
\lefteqn{\lRsys(t \mid \vec{t}^1, \ldots, \vec{t}^K)} \nonumber \\
 &= \min_{\PtZi{1}, \ldots, \PtZi{K}} \Rsys(t \mid \PtZi{1}, \ldots, \PtZi{K}, \vec{t}^1, \ldots, \vec{t}^K) \nonumber \\
 &= \min_{\nz_{1,t},\ldots,\nz_{K,t}} 
    \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K)
                                                 \prod_{k=1}^K P(C^k_t = l_k \mid \yktzl, \nktz, s^k_t) \nonumber \\
 &= \min_{\nz_{1,t},\ldots,\nz_{K,t}} 
    \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K) \times \nonumber \\ & \hspace*{12ex}
    \prod_{k=1}^K {m_k \choose l_k} \frac{B(l_k + \nn_{k,t}\ynl_{k,t}, m_k - l_k + \nn_{k,t}(1-\ynl_{k,t}))}
                                         {B(\nn_{k,t}\ynl_{k,t}, \nn_{k,t}(1-\ynl_{k,t}))} \,. \label{eq:LwrSysPost}
\end{align}
In the following, we will give some guidelines on how to choose the parameter sets $\PkZi{1}, \ldots, \PkZi{\tmax}$
which define the set of prior discrete reliability functions for components of type $k$.
We think this is much easier in terms of $\nz$ and $\yz$ than it would be in terms of $\alpha$ and $\beta$.
%***How to choose the sets of priors for the survival function of type $k$ components,
%i.e. how to choose $\PkZi{1}, \ldots \PkZi{\tmax}$?***

@@

%***code published in Louis' \textbf{R} package \texttt{ReliabilityTheory},

\subsection{Software}

The methods of this paper have been implemented in the \textbf{R}
\citep{R} package \texttt{ReliabilityTheory} \citep{2015:aslett-RT},
providing an easy to use interface for reliability practitioners.  The
primary function, which computes the upper and lower posterior
predictive system survival probabilities as in \eqref{eq:LwrSysPost}, is
named \texttt{nonParBayesSystemInferencePriorSets()}.  The user
specifies the times at which to evaluate the bounds, the survival
signature ($\Phi(\cdot)$), the component test data ($\vec{t}^1, \ldots,
\vec{t}^K$), and the prior parameter set for each component type and
time ($\PtZi{k}$, via $\nzu_{k,t}, \nzl_{k,t}, \yzu_{k,t}$, and
$\yzl_{k,t}$).  All computations of $\lRsys$
and $\uRsys$ at different time points are performed in parallel
automatically where the CPU has multiple cores.

Note that computation of the system signature itself can be simplified by
expressing the structure of the system as an undirected graph using the
\texttt{computeSystemSurvivalSignature()} function in the same package,
leaving only data and prior to be handled.  These publicly available
functions have been used in computing all the following examples for
reproducibility.  \ref{ap:software} details how to use this software.

\subsection{Examples}

@@

\section*{Appendix}
\appendix
\renewcommand*{\thesection}{\Alph{section}}
\section{Software details}
\label{ap:software}

Functions which make it easy to use the methods of this paper have been added to the \textbf{R} package \texttt{ReliabilityTheory} \citep{2015:aslett-RT}.  There are two functions of particular note: \texttt{computeSystemSurvivalSignature} and \texttt{nonParBayesSystemInferencePriorSets}

\subsection{Computing the survival signature}

The function \texttt{computeSystemSurvivalSignature} allows easy 
computation of the survival signature if the system is expressed as an
undirected graph with `start' and `terminal' nodes (which are not
considered components for survival signature computation).  The system
is considered to work if there is a path from the start to the terminal
node passing only through functioning components.

Graph representations of systems are most simply defined by using the 
\texttt{graph.formula} function.  The `start' node should be denoted
\texttt{s} and the `terminal' node should be denoted \texttt{t} and
intermediate nodes (representing actual components) should be numbered and
connected by edges denoted by \texttt{-}, where the numbering denotes physically
distinct components.  Component numbers can be repeated to include
multiple links.  For example, to build a simple three component series
system:

\noindent\texttt{sys <- graph.formula(s\,-\,1\,-\,2\,-\,3\,-\,t)}

and to build a three component parallel system:

\noindent\texttt{sys <- graph.formula(s\,-\,1\,-\,t, s\,-\,2\,-\,t, s\,-\,3\,-\,t)}

There is an additional shorthand which indicates a link exists to a list of multiple components separated by the \texttt{:} operator, so that the parallel system can be also be expressed more compactly by:

\noindent\texttt{sys <- graph.formula(s\,-\,1:2:3\,-\,t)}

Therefore, the simple bridge system of Figure \ref{fig:bridge-layout} can be constructed with:

\noindent\texttt{sys <- graph.formula(s\,-\,1\,-\,2\,-\,3\,-\,t, s\,-\,1\,-\,4\,-\,5\,-\,t, 2:4\,-\,6\,-\,3:5)}
\begin{itemize}
  \item \texttt{s\,-\,1\,-\,2\,-\,3\,-\,t} signifies the route from left to right entering the first component and going across the top of the system block diagram in Figure \ref{fig:bridge-layout};
  \item \texttt{s\,-\,1\,-\,4\,-\,5\,-\,t} signifies the bottom route through the block diagram;
  \item \texttt{2:4\,-\,6\,-\,3:5} connects the top two components of type 3 to the bottom two components of type 3, signifying the bridge.
\end{itemize}
Naturally such as expression is not necessarily unique, so that completely equivalently one may write:

\noindent\texttt{sys <- graph.formula(s\,-\,1\,-\,2:4\,-\,6\,-\,3:5\,-\,t, 2\,-\,3, 4\,-\,5)}

\

With the structure defined and the individual components numbered, it 
just remains to specify the types of each component.  This can be done
using the \texttt{setCompTypes} function.  This function takes the
system graph and a list of component type names and corresponding
component numbers.  Thus, completing the example for Figure
\ref{fig:bridge-layout}:
\noindent\texttt{sys <- setCompTypes(sys, list("T1"=c(1), "T2"=c(6),}

\noindent\texttt{~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~"T3"=c(2,3,4,5)))}

\

Computing the survival signature then involves a simple function call:
\noindent\texttt{survsig <- computeSystemSurvivalSignature(sys)}

\subsection{Computing sets of system survival probabilities}

*** to be completed
